% Author: Jonathan K. Kummerfeld
% File: acl19slate.tex

% Reviewer - Would it make sense to design some experiments to understand the learning curve? Terminal based tools usually take longer time for users to learn?
% Will     - Some commentary around how active learning might work would be welcome.

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl19slate}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{color}
\usepackage{enumitem}
\usepackage{xcolor,colortbl}
\usepackage{multicol}
\usepackage{subcaption}

% For printing, set hidelinks=true 
\hypersetup{pdftitle={Supplementary Note on "SLATE: A Super-Lightweight Annotation Tool for Experts"}
pdfauthor={Jonathan K. Kummerfeld},
pdfsubject={Natural Language Processing},
%%%colorlinks=true,
%%%plainpages=false,
%%%linktocpage=true,
%%%linkcolor=blue,% normal internal document links
%%%menucolor=blue,% colour for 'menu' links (not sure what these are, it matched linkcolor before)
%%%anchorcolor=black,% text of the anchor
%%%citecolor=gray,% bib refs
%%%urlcolor=gray,% URLs
pdfpagelayout=OneColumn}

% Set subref captions to have parentheses, e.g. (a) rather than a
\captionsetup{subrefformat=parens}

\newcommand{\myeg}{e.g.\@\xspace}
\newcommand{\myie}{i.e.\@\xspace}
\newcommand{\myvs}{vs.\@\xspace}
\newcommand{\tightparagraph}[1]{\noindent\textbf{#1}}
\newcommand{\slatecmd}[1]{\texttt{#1}}
\newcommand{\unixcmd}[1]{\texttt{#1}}

% To get URL breaking in bib working always
\def\UrlBreaks{\do\/\do-\do.}
%%%\setcounter{biburllcpenalty}{7000}
%%%\setcounter{biburlucpenalty}{8000}
%%%\setlength{\bibnamesep}{1.5\itemsep}

% Spacing beneath floats
\setlength{\dbltextfloatsep}{10pt}
\setlength{\textfloatsep}{10pt}
\setlength{\floatsep}{10pt plus 2pt minus 4pt}
\setlength{\textfloatsep}{10pt plus 2pt minus 4pt}
\setlength{\dblfloatsep}{\floatsep}
\setlength{\dbltextfloatsep}{10pt plus 2pt minus 4pt}
\setlength{\intextsep}{\floatsep}
\setlength{\abovecaptionskip}{8pt plus 3pt minus 2pt}

\setcounter{totalnumber}{500}
\setcounter{topnumber}{500}
\setcounter{bottomnumber}{500}
\renewcommand\floatpagefraction{.95}
\renewcommand\dblfloatpagefraction{.95} % for two column documents
\renewcommand\topfraction{.95}
\renewcommand\dbltopfraction{.95} % for two column documents
\renewcommand\bottomfraction{.95}
\renewcommand\textfraction{.05}

\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{12} %  Enter the acl Paper ID here

\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\Slate{\textsc{slate}\xspace}
\newcommand\slate{\textsc{slate}\xspace}

% Change description environments to use italics
\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\textit{#1}}

\title{Supplementary Note on "\slate: A Super-Lightweight Annotation Tool for Experts"}

\author{
  Jonathan K. Kummerfeld \\
  Computer Science \& Engineering \\
  University of Michigan \\
  Ann Arbor, MI, USA \\
  {\tt jkummerf@umich.edu}
}

\date{}

\begin{document}
\maketitle

After publishing the paper another tool named SLATE was brought to our attention.
This supplementary note is intended to recognise that work and clarify the different between the two tools.

The previous tool, "Segment and Link-based Annotation Tool, Enhanced", is a GUI web-based system that supports project management as well as annotation.
Implemented in Java, with a Flash-based front-end, it depends on Tomcat (a web server) and MySQL (a database management system).
It was first mentioned in \citet{prior-slate0} and then fully presented by \citet{prior-slate1}.
Code is available at \url{https://bitbucket.org/dainkaplan/slate/wiki/Home}.
Compared to our tool, the motivation and results are quite different.
They focus on providing an easy-to-use interface for non-expert computer users, while we focus on users comfortable in a terminal.
As a result, their tool involves more effort to set up, but then users can interact with it entirely through a web browser.

\bibliography{acl19slate}
\bibliographystyle{acl19slate}

\end{document}
